07_summary_stats

### 2023-08-08 07_summary_stats.Rmd
Update 07_summary_stats.Rmd
added

pct01_07 <- cbind(BB_pct01_07, TO_pct01_07) %>%
  select(., -3)
pct01_08 <- cbind(BB_pct01_08, TO_pct01_08) %>%
  select(., -3)
pct01_10 <- cbind(BB_pct01_10, TO_pct01_10) %>%
  select(., -3)
pct01_12 <- cbind(BB_pct01_12, TO_pct01_12) %>%
  select(., -3)
pct01_13 <- cbind(BB_pct01_13, TO_pct01_13) %>%
  select(., -3)
pct01_14 <- cbind(BB_pct01_14, TO_pct01_14) %>%
  select(., -3)
pct01_16 <- cbind(BB_pct01_16, TO_pct01_16) %>%
  select(., -3)
pct01_18 <- cbind(BB_pct01_18, TO_pct01_18) %>%
  select(., -3)
pct01_19 <- cbind(BB_pct01_19, TO_pct01_19) %>%
  select(., -3)
pct01_20 <- cbind(BB_pct01_20, TO_pct01_20) %>%
  select(., -3)
pct01_21 <- cbind(BB_pct01_21, TO_pct01_21) %>%
  select(., -3)
pct01_22 <- cbind(BB_pct01_22, TO_pct01_22) %>%
  select(., -3)
pct01_23 <- cbind(BB_pct01_23, TO_pct01_23) %>%
  select(., -3)
```

@@

Where are loudest sound levels?
```{r}
pct01_07 %>%
  summarise_if(is.numeric, list(~ min(., na.rm=TRUE)))

@@

@@

Where do we hear the most whale detections?
```{r}

Summary of each species: highest/lowest sound levels, number of detections
```{r}
allDrifts %>%

>>>>

# 1 Percentile
pct01_07 <- cbind(BB_pct01_07, TO_pct01_07) %>%
  select(., -3)
pct01_08 <- cbind(BB_pct01_08, TO_pct01_08) %>%
  select(., -3)
pct01_10 <- cbind(BB_pct01_10, TO_pct01_10) %>%
  select(., -3)
pct01_12 <- cbind(BB_pct01_12, TO_pct01_12) %>%
  select(., -3)
pct01_13 <- cbind(BB_pct01_13, TO_pct01_13) %>%
  select(., -3)
pct01_14 <- cbind(BB_pct01_14, TO_pct01_14) %>%
  select(., -3)
pct01_16 <- cbind(BB_pct01_16, TO_pct01_16) %>%
  select(., -3)
pct01_18 <- cbind(BB_pct01_18, TO_pct01_18) %>%
  select(., -3)
pct01_19 <- cbind(BB_pct01_19, TO_pct01_19) %>%
  select(., -3)
pct01_20 <- cbind(BB_pct01_20, TO_pct01_20) %>%
  select(., -3)
pct01_21 <- cbind(BB_pct01_21, TO_pct01_21) %>%
  select(., -3)
pct01_22 <- cbind(BB_pct01_22, TO_pct01_22) %>%
  select(., -3)
pct01_23 <- cbind(BB_pct01_23, TO_pct01_23) %>%
  select(., -3)

pct01_all <- rbind(pct01_07, pct01_08, pct01_10, pct01_12, pct01_13,
                   pct01_14, pct01_16, pct01_18, pct01_19, pct01_20,
                   pct01_21, pct01_22, pct01_23)
# need to add column with buoy name

# 99 Percentile
pct99_07 <- cbind(BB_pct99_07, TO_pct99_07) %>%
  select(., -3)
pct99_08 <- cbind(BB_pct99_08, TO_pct99_08) %>%
  select(., -3)
pct99_10 <- cbind(BB_pct99_10, TO_pct99_10) %>%
  select(., -3)
pct99_12 <- cbind(BB_pct99_12, TO_pct99_12) %>%
  select(., -3)
pct99_13 <- cbind(BB_pct99_13, TO_pct99_13) %>%
  select(., -3)
pct99_14 <- cbind(BB_pct99_14, TO_pct99_14) %>%
  select(., -3)
pct99_16 <- cbind(BB_pct99_16, TO_pct99_16) %>%
  select(., -3)
pct99_18 <- cbind(BB_pct99_18, TO_pct99_18) %>%
  select(., -3)
pct99_19 <- cbind(BB_pct99_19, TO_pct99_19) %>%
  select(., -3)
pct99_20 <- cbind(BB_pct99_20, TO_pct99_20) %>%
  select(., -3)
pct99_21 <- cbind(BB_pct99_21, TO_pct99_21) %>%
  select(., -3)
pct99_22 <- cbind(BB_pct99_22, TO_pct99_22) %>%
  select(., -3)
pct99_23 <- cbind(BB_pct99_23, TO_pct99_23) %>%
  select(., -3)
```

@@

Where are loudest sound levels?
```{r}
# For buoy 7
pct01_07 %>%
  summarise_if(is.numeric, list(~ min(., na.rm=TRUE)))

pct01_07 %>% filter(.$`BB_20-24000` > 120)

########################

pctlist <- c("07", "08", "10", "12", "14", "16", "18", "19",
             "20", "21", "22", "23")
# Doesn't show time stamp!
for (pc in pctlist) {
  data <- get(paste0("pct99_", pc)) %>%
    summarise_if(is.numeric, list(~ max(., na.rm=TRUE)))

  assign(paste0("max_", pc), data)
}

print(max_07)

## Add multi. Sum up rows and extract min/max
ggplot(data = TO_pct01_07, aes()) + 
  geom_histogram()

summary(TO_pct01_07)
```

@@

print(min_07)
```

Where do we hear the most whale detections? Which buoy had the most detections?
```{r}
# Summarize number of detections by species
allDrifts %>%
  group_by(species) %>%
  summarize(n())
## ZC had the most

#Which buoy had the most detections?
allDrifts %>%
  count(station, BWpresence) %>%
  filter(!BWpresence == 0) %>%
  arrange(desc(n))
## Buoy 18 has the most

#Plot buoys
ggplot() +
     geom_path(data=allDrifts, aes(x=Longitude, y=Latitude, group=factor(station), col=factor(station))) 
```

Summary of each species: highest/lowest sound levels, avg sound levels they're exposed to
```{r}
# Sort sperm whale detection by decreasing BB sound levels
allDrifts %>%
  dplyr::filter(species == "PM") %>%
  arrange(desc(BB_20.24000))

PM <- allDrifts %>%
  dplyr::filter(species == "PM")

print(paste("PM Max BB sound level: ", max(PM$BB_20.24000, na.rm = TRUE)))
print(paste("PM Min BB sound level: ", min(PM$BB_20.24000, na.rm = TRUE)))
print(paste("PM Max TOL125 sound level: ", max(PM$TOL_125, na.rm = TRUE)))
print(paste("PM Min TOL125 sound level: ", min(PM$TOL_125, na.rm = TRUE)))
print(paste("PM Max TOL20000 sound level: ", max(PM$TOL_20000, na.rm = TRUE)))
print(paste("PM Min TOL20000 sound level: ", min(PM$TOL_20000, na.rm = TRUE)))

# One detection value for BWC
BWC <- allDrifts %>%
  dplyr::filter(species == "BWC")
print(paste("BWC Max BB sound level: ", max(BWC$BB_20.24000, na.rm = TRUE)))
print(paste("BWC Min BB sound level: ", min(BWC$BB_20.24000, na.rm = TRUE)))
print(paste("BWC Max TOL125 sound level: ", max(BWC$TOL_125, na.rm = TRUE)))
print(paste("BWC Min TOL125 sound level: ", min(BWC$TOL_125, na.rm = TRUE)))
print(paste("BWC Max TOL20000 sound level: ", max(BWC$TOL_20000, na.rm = TRUE)))
print(paste("BWC Min TOL20000 sound level: ", min(BWC$TOL_20000, na.rm = TRUE)))

BB <- allDrifts %>%
  dplyr::filter(species == "BB")
print(paste("BB Max BB sound level: ", max(BB$BB_20.24000, na.rm = TRUE)))
print(paste("BB Min BB sound level: ", min(BB$BB_20.24000, na.rm = TRUE)))
print(paste("BB Max TOL125 sound level: ", max(BB$TOL_125, na.rm = TRUE)))
print(paste("BB Min TOL125 sound level: ", min(BB$TOL_125, na.rm = TRUE)))
print(paste("BB Max TOL20000 sound level: ", max(BB$TOL_20000, na.rm = TRUE)))
print(paste("BB Min TOL20000 sound level: ", min(BB$TOL_20000, na.rm = TRUE)))

BW37V <- allDrifts %>%
  dplyr::filter(species == "BW37V")
print(paste("BW37V Max BB sound level: ", max(BW37V$BB_20.24000, na.rm = TRUE)))
print(paste("BW37V Min BB sound level: ", min(BW37V$BB_20.24000, na.rm = TRUE)))
print(paste("BW37V Max TOL125 sound level: ", max(BW37V$TOL_125, na.rm = TRUE)))
print(paste("BW37V Min TOL125 sound level: ", min(BW37V$TOL_125, na.rm = TRUE)))
print(paste("BW37V Max TOL20000 sound level: ", max(BW37V$TOL_20000, na.rm = TRUE)))
print(paste("BW37V Min TOL20000 sound level: ", min(BW37V$TOL_20000, na.rm = TRUE)))

BW43 <- allDrifts %>%
  dplyr::filter(species == "BW43")
print(paste("BW43 Max BB sound level: ", max(BW43$BB_20.24000, na.rm = TRUE)))
print(paste("BW43 Min BB sound level: ", min(BW43$BB_20.24000, na.rm = TRUE)))
print(paste("BW43 Max TOL125 sound level: ", max(BW43$TOL_125, na.rm = TRUE)))
print(paste("BW43 Min TOL125 sound level: ", min(BW43$TOL_125, na.rm = TRUE)))
print(paste("BW43 Max TOL20000 sound level: ", max(BW43$TOL_20000, na.rm = TRUE)))
print(paste("BW43 Min TOL20000 sound level: ", min(BW43$TOL_20000, na.rm = TRUE)))

ZC <- allDrifts %>%
  dplyr::filter(species == "ZC")
print(paste("ZC Max BB sound level: ", max(ZC$BB_20.24000, na.rm = TRUE)))
print(paste("ZC Min BB sound level: ", min(ZC$BB_20.24000, na.rm = TRUE)))
print(paste("ZC Max TOL125 sound level: ", max(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Min TOL125 sound level: ", min(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Max TOL20000 sound level: ", max(ZC$TOL_20000, na.rm = TRUE)))
print(paste("ZC Min TOL20000 sound level: ", min(ZC$TOL_20000, na.rm = TRUE)))

```
Number of detections
```{r}
print(paste("Number of PM detections: ", nrow(PM)))
print(paste("Number of ZC detections: ", nrow(ZC)))
print(paste("Number of BW43 detections: ", nrow(BW43)))
print(paste("Number of BWC detections: ", nrow(BWC)))
print(paste("Number of BB detections: ", nrow(BB)))
print(paste("Number of BW37V detections: ", nrow(BW37V)))

#Plot
sp <- allDrifts %>% filter(!species == 'NA')
ggplot(sp, aes(species)) +
  geom_bar()
```
How do I find WHERE the highest/lowest detections are happening?
```{r}
ZC <- allDrifts %>%
  dplyr::filter(species == "ZC")

ZC[which.max(ZC$BB_20.24000),]
ZCmax2000 <- ZC[which.max(ZC$TOL_2000),]

#Point of ZC max TOL2000 sound level. Need to put in context of map.
ggplot(data = ZCmax2000, aes(x = Longitude, y = Latitude)) +
  geom_point()

#not working
allDrifts %>%
  group_by(species) %>%
  filter(max(allDrifts$BB_20.24000))

allDrifts %>%
  summarise_if(is.numeric, list(~ min(., na.rm=TRUE)))

@@
